---
title: "Model"
output:
  html_document:
    df_print: paged
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(stringr)
library(reshape2)
library(arsenal)
```

```{r, warning=FALSE, echo = FALSE, message=FALSE}
#Import cleaned data
imdb_model = 
  read_csv("./imdb_model.csv")

imdb_model = 
  imdb_model %>%
  mutate(
    num_genres = rowSums(imdb_model[,13:36]),
    mult_genre = ifelse(num_genres >1, 1, 0)
  )

imdb_model_genre = 
  imdb_model %>% 
  select(gross, Action: Film.Noir)

imdb_model_no_genre = 
  imdb_model %>% 
  select(-(Action: Film.Noir))
```

## Overview

We aimed to investigating factors that associated with the gross and how these factors influenced the gross. We hoped to construct a robust model that may potentially guide film industry investors to make wise decisions after the pandemic. Since the Exploratory Analyses Section didn't provide much information, we decided to build the best model, from the full model, without a predetermined hypothesis. 

After correlation matrices, genres in general didn't have strong associations with the gross but disturbed the effect of other predictors (not shown). Meanwhile, in a situation of investing, genres are usually predetermined. Thus, we decided to build two models: model 1 contained predictors other than genres and model 2 contained genres only. 

We used a stepwise regression method to find the best model. Stepwise regression is a "step by step" method to select predictors which have higher AIC scores. Finally, we presented two final models in the end of the section and discussed some interesting discoveries based on our models.  


```{r, warning=FALSE, include=FALSE, message=FALSE}
#function to plot heatmap
reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

 get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }
```


## Heatmap Plots of Correlation

### Heatmap for Genres

```{r, warning=FALSE, echo = FALSE, message=FALSE}
#heatmap for genre
cor.mat.heat.genre <- round(cor(imdb_model_genre),2)
melted_cormat.genre <- melt(cor.mat.heat.genre)

cor.mat.heat.genre <- reorder_cormat(cor.mat.heat.genre)
upper_tri.heat.genre <- get_upper_tri(cor.mat.heat.genre)

# Melt the correlation matrix
melted_cormat_up_genre <- melt(upper_tri.heat.genre, na.rm = TRUE)

# Create a ggheatmap
ggheatmap_genre =
  ggplot(melted_cormat_up_genre, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
    midpoint = 0, limit = c(-1,1), space = "Lab", 
    name="Pearson\nCorrelation") +
  theme_minimal()+ # minimal theme
  theme(axis.text.x = element_text(angle = 90, 
    size = 10, hjust = 1, vjust = 0))+
  coord_fixed()+
  labs(
    title = "Figure 1. Heatmap of Gross and Genres",
    x = "",
    y = ""
  )

res_cor_up_genre = 
melted_cormat_up_genre %>%
  filter(
    Var1 == "gross"
  ) %>%
  pivot_wider(
    names_from = Var2,
    values_from = value
  ) %>%
  rename(
    " "=Var1
  ) %>%
  select(
    -gross
  )

ggheatmap_genre
```

```{r,echo = FALSE, fig.cap= "Table 1. Correlations between Gross and all Genres"}
res_cor_up_genre
```

Figure 1 presented the correlation matrix between various genres and gross. From the heatmap, we can intuitively observe associations between genres and gross. Overall, we didn't observe any strong connections between genres and gross. Among all genres, adventure, fantasy, animation, family, action and science fiction have stronger associations with gross and they may contribute to the model later. 


### Heatmap for non-Genre Factors 

```{r, warning=FALSE, echo=FALSE, message=FALSE}
#heatmap for no genre
cor.mat.heat.nogenre <- round(cor(imdb_model_no_genre,use = "complete.obs"),2)
melted_cormat.nogenre <- melt(cor.mat.heat.nogenre)

cor.mat.heat.nogenre <- reorder_cormat(cor.mat.heat.nogenre)
upper_tri.heat.nogenre <- get_upper_tri(cor.mat.heat.nogenre)

# Melt the correlation matrix
melted_cormat_up_nogenre <- melt(upper_tri.heat.nogenre, na.rm = TRUE)

# Create a ggheatmap
ggheatmap_nogenre =
  ggplot(melted_cormat_up_nogenre, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
    midpoint = 0, limit = c(-1,1), space = "Lab", 
    name="Pearson\nCorrelation") +
  theme_minimal()+ # minimal theme
  theme(axis.text.x = element_text(angle = 90, 
    size = 10, hjust = 1, vjust = 0))+
  coord_fixed()+
  labs(
    title = "Figure 2. Heatmap of Gross and non-Genre Factors",
    x = "",
    y = ""
  )

res_cor_up_nogenre = 
melted_cormat_up_nogenre %>%
  filter(
    Var1 == "gross"
  ) %>%
  pivot_wider(
    names_from = Var2,
    values_from = value
  ) %>%
  rename(
    " "=Var1
  ) %>%
  select(
    -gross
  )

ggheatmap_nogenre

```

```{r,echo = FALSE, , fig.cap= "Table 2. Correlations between Gross and non-Genre Factors"}
res_cor_up_nogenre
```

Figure 2 presented the correlation matrix between other factors and gross. We observed a better and stronger associations. Among all predictors, number of voted users, number of users for reviews, duration, IMDB scores, budget and number of genres have stronger associations with gross and they might contribute to the model later. 


## Model Building

We applied `regsubsets` from `leap` library to conduct the regression. Basically, this function constructs the null model first (contains only intercept) and combines various of variables to form an exhaustive subset of models. Within the subset, the function will compare the adjusted R2 and find the best combination of predictors. It is a better method than stepwise selection but needs a longer calculation time. Also, since cross validation has been done within the function, we don't need to perform the cross validation. Because we don't have many features, we decided to utilize this method to select the best model.

### Model without Genres

```{r, warning=FALSE, include=FALSE, message=FALSE}
#model without genres 
lm.leaps_no_genre = 
  leaps::regsubsets(gross~., data = imdb_model_no_genre, nvmax = 8,
                     method = "seqrep")
sum.no_genre = summary(lm.leaps_no_genre)
```

```{r,echo = FALSE}
plot(sum.no_genre$adjr2,xlab='No. of Variables',ylab='Adj. R^2',type='l', main = "Figure 3. Plot of Number of Variables for non-Genre Model")
```
```{r,echo = FALSE}
plot(lm.leaps_no_genre,scale = "adjr2", main = "Figure 4. Plot of Important Variables for non-Genre Model")
```
  
  Figure 3 showed how many variables should the best model included. In our case, including 8 variables will make our model reach the highest accuracy (highest adjusted R2). 
  
  From Figure 4, we can conclude our model should include following variables: number of critics for reviews, Facebook likes of the director, Facebook likes of the primary actor/actress, number of voted users, total Facebook likes of the cast, number of users for reviews, IMDB score and the number of genres.
  
#### non-Genre Model

```{r, warning=FALSE, include=FALSE, message=FALSE}
#final model according to the selection
lm.no_genre = lm(gross ~ num_critic_for_reviews + director_facebook_likes + actor_1_facebook_likes + num_voted_users + cast_total_facebook_likes +  num_user_for_reviews + imdb_score + num_genres, data = na.omit(imdb_model_no_genre))
```

```{r,echo = FALSE, fig.cap= "Table 3. Estimates and P.values of the non-Genre Model"}
lm.no_genre %>%
  broom::tidy() %>%
  select(
    term, estimate, p.value
  ) %>%
  knitr::kable(digits = 3)
```



### Model of Genres

```{r, warning=FALSE, include=FALSE, message=FALSE}
#stepwise with genres
lm.leaps_genre = leaps::regsubsets(gross~., data = imdb_model_genre, nvmax = 8,
                     method = "seqrep")
sum.genre = summary(lm.leaps_genre)
```

```{r,echo = FALSE}
plot(sum.genre$adjr2,xlab='No. of Variables',ylab='Adj. R^2',type='l',main = "Figure 5. Plot of Number of Variables for Genre Model")
plot(lm.leaps_genre,scale = "adjr2", main = "Figure 6. Plot of Important Varialbes for Genre Model")
```
  
Similarly, 8 variables should be included in our model according to Figure 5. From the Figure 6, we can conclude Action, Adventure, Fantasy, Sci-Fiction, Family, Drama, Horror and Documentary are important factors that influence the gross. However, since the accuracy (adjusted R2) is small, genre in general may not be an important factor to consider.

#### Genre Model

```{r, warning=FALSE, include=FALSE, message=FALSE}
lm.genre = 
  lm(gross ~ Action+ Adventure + Fantasy + Sci.Fi + Family + Drama + Horror + Documentary, data = na.omit(imdb_model_genre))
```

```{r,echo = FALSE}
lm.genre %>%
  broom::tidy() %>%
  select(
    term, estimate, p.value
  ) %>%
  knitr::kable(digits = 3)
```


## Stratification

```{r}
imdb_model_action = 
  imdb_model %>% 
  select(
    -(Adventure:mult_genre)
  ) %>%
  filter(
    Action == 1
  )
  
lm.action = lm(gross ~ num_critic_for_reviews + director_facebook_likes + actor_1_facebook_likes + num_voted_users + cast_total_facebook_likes +  num_user_for_reviews + imdb_score, data = na.omit(imdb_model_action))

lm.action %>%
  broom::tidy() %>%
  select(
    term, estimate, p.value
  ) %>%
  knitr::kable(digits = 3)

lm.no_genre %>%
  broom::tidy() %>%
  select(
    term, estimate, p.value
  ) %>%
  knitr::kable(digits = 3)
```



## Diagnosis
```{r, echo= FALSE, , fig.cap= "Figure 7-10. Plots to Check the Assumptions after Transformation"}
par(mfrow=c(2,2))
plot(lm.no_genre)
```


Above provides assumption checking of the non-genre model. Since the non-Genre Model has a much higher accuracy, we check the assumption of it. Unfortunately, plots are not satisfactory. 

* A cluster of data locates mainly on the left and is not randomly distributed for the Residuals vs Fitted plot. However, other clear pattern is not observed, meaning that linear regression is still appropriate. 

* Normal QQ plot provides insight of its normality and the majority of our model lied on the line, which is acceptable. 

* For scale location plot, a cluster of data aggregates together showed the equal variance assumption was violated. 

* Lastly, we can observe some outliers that are influential from the Residuals vs Leverage plot.

Since nearly all the assumptions were violated in some extent, we decided to perform a box-cox transformation.

### Box-Cox Transformation

Box-Cox transformation is another common method to normalize the data. Detailed information is provided [here](https://rss.onlinelibrary.wiley.com/doi/abs/10.1111/j.2517-6161.1964.tb00553.x). We performed Box-Cox transformation to our non-Genre model and check the assumptions again. 

```{r, echo= FALSE, fig.cap= "Figure 11. Fitted Lambda for Box-Cox Transformation."}
#find lambda for our model.
boxcox.lm = MASS::boxcox(lm.no_genre)
lambda <- boxcox.lm$x[which.max(boxcox.lm$y)]
```

Above provides the fitted lambda for the transformation and we transformed our model based on this lambda, which was `r round(lambda, digits = 3)`. 

### Assumption Checking after Transformation

```{r, echo=FALSE , fig.cap= "Figure 12-15. Plots to Check the Assumptions after Transformation"}
lm.no_genre_lambda = lm(gross^lambda ~ num_critic_for_reviews + director_facebook_likes + actor_1_facebook_likes + num_voted_users + cast_total_facebook_likes +  num_user_for_reviews + imdb_score + num_genres, data = na.omit(imdb_model_no_genre))
par(mfrow=c(2,2))
plot(lm.no_genre_lambda)
```

Above presents the check of assumption after transformation. In general, Box-Cox transformation provided a quite satisfactory transformation to our model. 

* A cluster of data still exists on the left and is more randomly distributed compared the plot before transformation.However, a long "tail" on the right suggests a strong influence of outliers. 

* Transformed model lies on the line perfectly. 

* For scale location plot, a cluster of data aggregates together but the trend line is more horizontal than the previous scale location plot, showing that the homoskedasticity (equal spread of the data) is checked for the majority of the data. 

* Lastly, we can still observe some outliers that are influential from the Residuals vs Leverage plot.




## Conclusion and Discussion

















